GNSS displacement detection based on Bayesian inference

### 2020-11-13 paper/manuscript.tex
add new action

\begin{equation}\label{eq_bayesian_prior_tau_4}
P({\bf{\tau }}) = P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}
\begin{equation}\label{eq_bayesian_prior_tau_5}
P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}

@@

\subsection{Displacement Extraction}

>>>>

\begin{equation}\label{eq_bayesian_prior_tau_4}
P({\bf{\tau }}) = P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}
Continue to expand in a similar way, and finally get

\begin{equation}\label{eq_bayesian_prior_tau_5}
P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
\end{equation}
Through \ref{eq_bayesian_prior_tau_basic} and \ref{eq_bayesian_prior_tau_5}, the joint probability of all change points can be determined. Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.

@@
